%% invoking.tex
%% Created by Laurence D. Finston (LDF) Wed 19 Jan 2022 06:20:03 AM CET

\input tugboat.sty

\title * Invoking \MP\/ and \TeX\/ indirectly from GNU 3DLDF *
\author * Laurence Finston *
\address * Germany *
\netaddress * Laurence.Finston@gmx.de *
\article
\head * Introduction *
GNU 3DLDF is a package for three-dimen\-sion\-al draw\-ing with \MF\/ or \MP\/ output.
It implements a language based on the \MF\/ language with many additional data types
and operations.

Even in 3D, many objects in a drawing are likely to be planar.  In this case, it can be useful to use
\MF\/ or \MP\/ to apply operations that aren't implemented in 3DLDF to these objects.  Another
application for this technique is to invoke \TeX\/, directly or via \MP\/, in order to obtain information
about matters pertaining to typesetting, e.g., the size or bounding boxes of glyphs or the width, height
and depth of boxes.

\head * Paths in \MF\/ and 3DLDF*

In \MF\/, {\bf paths} are represented as B{\'e}zier curves consisting of points ({\bf pairs})
and {\it connectors}. The most basic connector is |..| and connectors may be modified in various ways
using |curl|, |dir|, |tension| or a |pair| representing a direction vector.  Ultimately, all connectors
are converted to the form ``|.. controls <pair> and <pair> ..|'', which the user may also specify directly.
This is the form used when showing a {\bf path}:

%% Make example.

In 3DLDF, {\bf paths} are also represented as points (in this case,
the data type is |point| rather than |pair|) and connectors, but not
as B{\'e}zier curves.  In the past, 3DLDF only implemented the connectors ``|..|'', ``|...|''
and ``|--.|'' and they were merely |strings| that were passed to the \MP\/ output and not processed
internally within 3DLDF in any way.



\head * Measuring text *

\head * Directions and directiontimes of paths *


\head * Obtaining paths for glyphs *

\head * Resolving paths *


\head * Conclusion *

\makesignature

\bye

%% Local Variables:
%% mode:plain-TeX
%% auto-fill-function:nil
%% End:
